---
title: "Hospital and Health Care in India"
author: "Ashutosh"
date: "1/12/2018"
output: html_document
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Hospital and HealthCare in India

This project is to gain an insights on the hospital location and healthcare in India. It's a continuing project and we will just do an Exploratory Data Analysis of the datasets we can find

```{r packages, echo=FALSE}
library(dplyr)
library(ggplot2)
library(ggmap)

```

#### The data 

We have a hospital directory of all the hospitals in India. Let's load it 

```{r dataset, echo=FALSE}

hospitals = read.csv('hospital.csv')

```

```{r, echo=FALSE}
head(hospitals)
str(hospitals)
nrow(hospitals)
ncol(hospitals)
```

So there are 23584 hospitals in this dataset and each hospital has 48 pieces of information. Let's take a look at the columns 

```{r, echo=FALSE}
colnames(hospitals)
```

```{r, echo=FALSE}
sapply(hospitals, function(x) sum(is.na(x)) )
```

Since there are many columns which have missing value and we don't know about the dataset yet. Let's take a look at the columns 1 by one. First one is Hospital Category

```{r, echo=FALSE}
# colnames(hospitals)
summary(hospitals$Hospital_Category)
```

We see that many of the missing values are present and we have generally 2 values  Private, Public/Government. Now let's take a look the names of hospitals which are set to 0 

```{r, echo=FALSE}
z0_hospitals = subset(hospitals,Hospital_Category == 0)
head(z0_hospitals$Hospital_Name)
```

These  names look like private hospitals But we can't say for sure. For the time Being we will set the values as N/As

```{r, echo=FALSE}
hospitals[,"Hospital_Category"][hospitals[,"Hospital_Category"] == 0] <- NA
summary(hospitals$Hospital_Category)
```

